Traffic aware Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems

### 2014-10-01 Report/mse_formulation.tex
temporary-commit

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{rCl} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \nonumber \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{IEEEeqnarray}
}
where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \dfrac{1}{1 + \gamma_{l,k,n}}
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad &  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& \qquad \quad {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}
where \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation and \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}}.

@@

Now, using the above approximation for the rate constraint, the problem defined by \eqref{eqn-mse-1} can be solved optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}} for the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
	\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
	& \quad & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	&\quad& + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n} \eqsub \label{eqn-mse-2.3}
\end{IEEEeqnarray}
}
\subsubsection*{Convergence}
Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point of the original nonconvex problem at each iteration. The uniqueness of the transmit and the receive precoders are justified if the phase ambiguity from the stationary solution is eliminated. It can be seen from the \ac{MSE} expression \eqref{eqn-mse-2.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-2.3} as
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{multline}
}
At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing the weighted \ac{MSE} criterion due to the convex nature of the relaxed problem. Upon finding the optimal transmit precoders, the receive beamformers are updated using the \ac{MMSE} receivers. The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders thereby leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.

>>>>

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{rCl} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \nonumber \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
\end{IEEEeqnarray}
}
where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \dfrac{1}{1 + \gamma_{l,k,n}}
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad &  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}
where \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation and \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}}.

@@

Now, using the above approximation for the rate constraint, the problem defined by \eqref{eqn-mse-1} can be solved optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}} for the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin} \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
\subsubsection*{Convergence}
Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point of the original nonconvex problem at each iteration. The uniqueness of the transmit and the receive precoders are justified if the phase ambiguity from the stationary solution is eliminated. It can be seen from the \ac{MSE} expression \eqref{eqn-mse-1.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-1.3} as
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{multline}
}
At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing the weighted \ac{MSE} criterion due to the convex nature of the relaxed problem. Upon finding the optimal transmit precoders, the receive beamformers are updated using the \ac{MMSE} receivers. The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders thereby leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.

### 2014-10-01 Report/primal_approach.tex
temporary-commit

The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}. Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence. The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same. 
%Much of the details are provided in the Appendix \ref{a-2}.

>>>>

The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}. Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} in \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration until convergence. The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same. 
%Much of the details are provided in the Appendix \ref{a-2}.

### 2014-10-01 Report/simulation_distributed.tex
Updated double column
temporary-commit

The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms. The performance is compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d-1} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update. Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

The Fig. \ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points. In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations to exchange either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme. In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. It can be seen from Fig. \ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-3-1}
\label{fig-d-1}
}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-5-1}
\label{fig-d-2}
}
\caption{Number of backlogged packets at each \ac{SCA} points}
\label{fig-d}
\end{figure*}

In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary experiencing the path loss following the uniform distribution between \me{[0,-6]} dB. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
% \begin{figure*}
% \centering
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-5}
% \caption{Queue deviation}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-6}
% \caption{Sum rate performance}
% \end{subfigure}
% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
% \label{fig-d-2}
% \end{figure*}

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-9-2-1}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3.1}
\end{figure}

>>>>

The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

The Fig. \ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points. In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables. In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. It can be seen from Fig. \ref{fig-d} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.

\iftoggle{enable_dist_fig}
{	
In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to have the path loss following the uniform distribution between \me{[0,-6]} dB from all \acp{BS}. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
\begin{figure*}
	\centering
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-3-2}
		\label{fig-d-1}
	}
	\hfill
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-5-1}
		\label{fig-d-2}
	}
	\caption{Number of backlogged packets at each \ac{SCA} points}
	\label{fig-d}
\end{figure*}
% \begin{figure*}
% \centering
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-5}
% \caption{Queue deviation}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-6}
% \caption{Sum rate performance}
% \end{subfigure}
% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
% \label{fig-d-2}
% \end{figure*}
}{
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{fig-3-2}
\label{fig-d-1}
\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}}
\label{fig-d}
\end{figure}
}
Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
	\label{fig-d-3.1}
\end{figure}
